### 2014-12-09 Draft/introduction.tex
minor

\begin{itemize}
	\item An ML and NLP-based approach that effectively infers formal temporal constraints of method invocations. 
	%To the best of our knowledge, our approach is the first one to apply NLP for inferring temporal constraints from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}, along with the experimental subjects and the results. 
	\item An evaluation of our approach on the \amazonAPI, the \paypalAPI, and the commonly used package \CodeIn{java.io} from the JDK API. 
\end{itemize}

>>>>

\begin{itemize}
	\item An ML and NLP-based approach that effectively infers formal temporal constraints of method invocations. 
	%To the best of our knowledge, our approach is the first one to apply NLP for inferring temporal constraints from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
	All our experimental subjects, results, and artifacts are publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}. 
	\item An evaluation of our approach on the \amazonAPI, the \paypalAPI, and the commonly used package \CodeIn{java.io} from the JDK API. 
\end{itemize}
